refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-10-30 paper/manuscript.tex
PAPER: begin changes requested by referee

Given the number of publications arising from the reflectometry technique, it is vital that both the experiments and analyses are reproducible.
Reproducibility in research is an underlying principle of science; unfortunately, it is not always possible to reproduce the results of others \cite{Stark2018}, because there is frequently not enough information provided in journal articles to repeat the analyses. Even if the datasets and software packages used to analyse them are supplied in supporting information (most often they are not), a comprehensive, ordered, set of instructions or a codified workflow would need to be provided \cite{Moeller2017a}.
One example for addressing this reproducibility issue is the set of guidelines from the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010}.

@@

The posterior probability, $p(\theta | I, D)$, describes the distribution of parameter values consistent with the data and prior information. In the simplest form, this is akin to a confidence interval for a parameter derived by least-squares analysis. However, when parameters are correlated, or two models give similar quality of fit (`multi-modality'), a simple confidence interval can be misleading.
The posterior probability is derived by encoding the likelihood and prior distributions and then using an MCMC algorithm (via the \emcee\ and \ptemcee\ packages) to perform affine invariant ensemble sampling \cite{emcee, ptemcee}.
At the end of an MCMC run, the parameter set possesses a number of samples (called a `chain'); the samples reveal the distribution and covariance of the parameters, the spread of the model-predicted measurements around the data, and in a reflectometry context, the range of SLD profiles that are consistent with the data.
The chain statistics are used to update each \Parameter\ value, and assign a standard uncertainty. For the sampling, these represent the median and half the $[15.87, 84.13]$ percentile range respectively; the latter approximating the standard deviation for a normally distributed statistic.

@@

\refnx\ is released under the BSD permissive open source licence. In addition, all of the  dependencies of \refnx\ are released under open source licences which means that use is free of cost to the end user and, more importantly, the user user is free to modify, improve, and inspect this software.

>>>>

Given the number of publications arising from the reflectometry technique, it is vital that both the experiments and analyses are reproducible.
Reproducibility in research is an underlying principle of science; unfortunately, it is not always possible to reproduce the results of others \cite{Stark2018}, because there is frequently not enough information provided in journal articles to repeat the analyses. Even if the datasets and software packages used to analyse them are supplied in supporting information (most often they are not), a comprehensive, ordered, set of instructions or a codified workflow would need to be provided \cite{Moeller2017a}.
One example for addressing this reproducibility issue is the set of guidelines from the small-angle scattering community for the deposition of data and and associated models \cite{Trewhella:jc5010, pauw2013}.

@@

The posterior probability, $p(\theta | D, I)$, describes the distribution of parameter values consistent with the data and prior information. In the simplest form, this is akin to a confidence interval for a parameter derived by least-squares analysis. However, when parameters are correlated, or two models give similar quality of fit (`multi-modality'), a simple confidence interval can be misleading.
The posterior probability is derived by encoding the likelihood and prior distributions and then using an MCMC algorithm (via the \emcee\ and \ptemcee\ packages) to perform affine invariant ensemble sampling \cite{emcee, ptemcee}.
At the end of an MCMC run, the parameter set possesses a number of samples (called a `chain'); the samples reveal the distribution and covariance of the parameters, the spread of the model-predicted measurements around the data, and in a reflectometry context, the range of SLD profiles that are consistent with the data.
The chain statistics are used to update each \Parameter\ value, and assign a standard uncertainty. For the sampling, these represent the median and half the $[15.87, 84.13]$ percentile range respectively; the latter approximating the standard deviation for a normally distributed statistic.

@@

\refnx\ is released under the BSD permissive open source licence. In addition, all of the  dependencies of \refnx\ are released under open source licences which means that use is free of cost to the end user and, more importantly, the user is free to modify, improve, and inspect this software.
